Abstract Binding Trees

### 2015-11-05 paper.tex
Comment line endings
Set mode to draft by default
Update paths to agda latex output

\documentclass[11pt]{article}

@@

% fonts
\usepackage[
  activate={true,nocompatibility},
  final,
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

% make lualatex play nice with agda
\makeatletter
\ifluatex
   \newwrite\CATCHPATCHOUT
\fi
\def\CatchFBT@Fin@l#1[#2]{%
   \begingroup
      \endlinechar\m@ne \makeatletter #2%
      \ifluatex
         \immediate\openout\CATCHPATCHOUT=\jobname.catchpatch
         \immediate\write\CATCHPATCHOUT {\CatchFBT@tok{\the\CatchFBT@tok}}%
         \immediate\closeout\CATCHPATCHOUT
         \@@input \jobname.catchpatch
      \else
      \scantokens\expandafter{%
         \expandafter\CatchFBT@tok\expandafter{\the\CatchFBT@tok}}%
      \fi
      \CatchFBT@IsAToken{#1}
         {\global#1\expandafter{\the\CatchFBT@tok}}
         {\xdef#1{\the\CatchFBT@tok}}%
      \ifx\CatchFBT@tok#1\else\global\CatchFBT@tok{}\fi
   \endgroup
}% \CatchFBT@Final
\makeatother

@@

\newcommand\MkValence[3]{%
  \ifthenelse{\equal{#1}{}}{}{%
    \{#1\}%
  }%
  \ifthenelse{\equal{#2}{}}{}{%
    [#2]%
  }.\, #3
}
\newcommand\MkBTm[3]{\{#1\}[#2].\, #3}
\newcommand\MkArity[2]{(#1)\, #2}
\newcommand\IsArity[1]{\IMode{#1}\ \textit{arity}}
\newcommand\IsValence[1]{\IMode{#1}\ \textit{valence}}
\newcommand\IsSort[1]{\IMode{#1}\ \textit{sort}}
\newcommand\Leq[2]{\IMode{#1}\leq\IMode{#2}}

@@

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\left\langle #1, #2 \right\rangle}
\newcommand\Tuple[1]{\left\langle #1 \right\rangle}
\newcommand\FLift[2]{
  \Operators\langle#1%
  \ifthenelse{\equal{#2}{}}{}{, #2}\rangle
}
\newcommand\PairTimes[2]{\langle #1\, {\scriptstyle {{\times}}}\, #2 \rangle}
\newcommand\SSingleton{\bullet}
\newcommand\Forget[1]{|\, #1\, |}

@@

\newcommand\Rename[2]{
  #2\upharpoonright #1
}
\newcommand\IsRenaming[3]{
  \Rename{\IMode{#1}}{\IMode{#2}}%
  \leadsto\OMode{#3}%
}

\newcommand\Subst[3]{
  \left[#1\, /\, #2\right]#3%
}

@@

@@

Let $\Define{V_s(\Upsilon\parallel\Gamma)}{\MkSet{x\in\Dom\Gamma\mid
\Gamma(x)=s}}$ be called the presheaf of variables; additionally, we have a
presheaf of symbols
$\Define{S_s(\Upsilon\parallel\Gamma)}{\MkSet{u\in\Dom\Upsilon\mid
\Upsilon(x)=s}}$. For an object $\Of{P}{\widehat{\HypCat}^\Sorts}$, we will
use the notation $P^{[\Gamma]}$ to mean $\prod_{x\in\Dom\Gamma}P_{\Gamma(x)}$;
likewise, $S^{\{\Upsilon\}}$ shall mean
$\prod_{u\in\Dom\Upsilon}S_{\Upsilon(u)}$.

@@

For each signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we have an
endofunctor
$\Of{\SigFun{\Sigma}}{\widehat{\HypCat}^\Sorts\to\widehat{\HypCat}^\Sorts}$,
which is defined as follows:

\begin{align*}
  \IMode{\SigFun{\Sigma}(X)_s(\Upsilon\parallel\Gamma)}
    &\triangleq
    \OMode{
      \coprod_{\vartheta\in\Operators\Pair{\Upsilon}{\MkArity{\vec{v}}{s}}}
      \prod_{\MkValence{\vec{p}}{\vec{q}}{s'}\in\vec{v}}
      X_{s'}(\Upsilon,\vec{p}\parallel\Gamma,\vec{q})
    }
\end{align*}

\begin{remark}
  By $\Upsilon,\vec{p}$ we mean any extension of $\Upsilon$ by fresh symbols $\vec{u}$ of sorts $\vec{p}$.
\end{remark}

@@

\CatchFileBetweenTags\tmp{latex/Code.tex}{agda}

@@

\ExecuteMetaData[latex/Code.tex]{lang}\\

\ExecuteMetaData[latex/Code.tex]{lan}

@@

\ExecuteMetaData[latex/Code.tex]{rang}\\

\ExecuteMetaData[latex/Code.tex]{ran}

@@

\ExecuteMetaData[latex/Code.tex]{var}\\

\ExecuteMetaData[latex/Code.tex]{sym}

@@

\ExecuteMetaData[latex/Code.tex]{ctx}\\

\ExecuteMetaData[latex/Code.tex]{sctx}\\

\ExecuteMetaData[latex/Code.tex]{ctxdom}\\

\ExecuteMetaData[latex/Code.tex]{ctxidx}\\

\ExecuteMetaData[latex/Code.tex]{elem}

@@

\ExecuteMetaData[latex/Code.tex]{sign}

@@

\ExecuteMetaData[latex/Code.tex]{trees}

@@

\ExecuteMetaData[latex/Code.tex]{H}\\

\ExecuteMetaData[latex/Code.tex]{HHat}\\

\ExecuteMetaData[latex/Code.tex]{V}\\

\ExecuteMetaData[latex/Code.tex]{tensor0}\\

\ExecuteMetaData[latex/Code.tex]{tensor1}\\

\ExecuteMetaData[latex/Code.tex]{extension}

>>>>

\documentclass[draft,11pt]{article}

@@

% fonts
\usepackage[
  activate={true,nocompatibility},
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

% make lualatex play nice with agda
\makeatletter
\ifluatex
   \newwrite\CATCHPATCHOUT
\fi
\def\CatchFBT@Fin@l#1[#2]{%
   \begingroup%
      \endlinechar\m@ne \makeatletter #2%
      \ifluatex%
         \immediate\openout\CATCHPATCHOUT=\jobname.catchpatch%
         \immediate\write\CATCHPATCHOUT {\CatchFBT@tok{\the\CatchFBT@tok}}%
         \immediate\closeout\CATCHPATCHOUT%
         \@@input \jobname.catchpatch%
      \else%
      \scantokens\expandafter{%
         \expandafter\CatchFBT@tok\expandafter{\the\CatchFBT@tok}}%
      \fi%
      \CatchFBT@IsAToken{#1}%
         {\global#1\expandafter{\the\CatchFBT@tok}}%
         {\xdef#1{\the\CatchFBT@tok}}%
      \ifx\CatchFBT@tok#1\else\global\CatchFBT@tok{}\fi%
   \endgroup%
}% \CatchFBT@Final
\makeatother

@@

\newcommand\MkValence[3]{%
  \ifthenelse{\equal{#1}{}}{}{%
    \{#1\}%
  }%
  \ifthenelse{\equal{#2}{}}{}{%
    [#2]%
  }.\, #3%
}
\newcommand\MkBTm[3]{\{#1\}[#2].\, #3}
\newcommand\MkArity[2]{(#1)\, #2}
\newcommand\IsArity[1]{\IMode{#1}\ \textit{arity}}
\newcommand\IsValence[1]{\IMode{#1}\ \textit{valence}}
\newcommand\IsSort[1]{\IMode{#1}\ \textit{sort}}
\newcommand\Leq[2]{\IMode{#1}\leq\IMode{#2}}

@@

\newcommand\Grothendieck[2]{\oint^{#1} #2#1}
\newcommand\Pair[2]{\left\langle #1, #2 \right\rangle}
\newcommand\Tuple[1]{\left\langle #1 \right\rangle}
\newcommand\FLift[2]{
  \Operators\langle#1%
  \ifthenelse{\equal{#2}{}}{}{, #2}\rangle%
}
\newcommand\PairTimes[2]{\langle #1\, {\scriptstyle {{\times}}}\, #2 \rangle}
\newcommand\SSingleton{\bullet}
\newcommand\Forget[1]{|\, #1\, |}

@@

\newcommand\Rename[2]{%
  #2\upharpoonright #1%
}
\newcommand\IsRenaming[3]{%
  \Rename{\IMode{#1}}{\IMode{#2}}%
  \leadsto\OMode{#3}%
}

\newcommand\Subst[3]{%
  \left[#1\, /\, #2\right]#3%
}

@@

Let $\Define{V_s(\Upsilon\parallel\Gamma)}{\MkSet{x\in\Dom\Gamma\mid
\Gamma(x)=s}}$ be called the presheaf of variables; additionally, we have a
presheaf of symbols
$\Define{S_s(\Upsilon\parallel\Gamma)}{\MkSet{u\in\Dom\Upsilon\mid
\Upsilon(x)=s}}$. Lastly, we have the presheaf of operators with arity $a$,
$\Define{\Operators_a(\Upsilon\parallel\Gamma)}{\Operators\Pair{\Upsilon}{a}}$

@@

For an object $\Of{P}{\widehat{\HypCat}^\Sorts}$, we will use the notation
$P^{[\Gamma]}$ to mean $\prod_{x\in\Dom\Gamma}P_{\Gamma(x)}$; likewise,
$S^{\{\Upsilon\}}$ shall mean $\prod_{u\in\Dom\Upsilon}S_{\Upsilon(u)}$.

@@

For each signature $\Match{\Sigma}{\Pair{\Sorts}{\Operators}}$, we have an
endofunctor
$\Of{\SigFun{\Sigma}}{\widehat{\HypCat}^\Sorts\to\widehat{\HypCat}^\Sorts}$,
which is defined as follows:
\begin{align*}
  \IMode{\SigFun{\Sigma}(X)_s}
    &\triangleq
    \OMode{
      \coprod_{\vartheta\in \Operators_{\MkArity{\vec{v}}{s}}}
      \prod_{\MkValence{\vec{p}}{\vec{q}}{s'}\in\vec{v}}
      X_{s'}^{\Yoneda{\vec{p}\parallel\vec{q}}}
    }
\end{align*}

@@

\CatchFileBetweenTags\tmp{Code.tex}{agda}

@@

\ExecuteMetaData[Code.tex]{lang}\\

\ExecuteMetaData[Code.tex]{lan}

@@

\ExecuteMetaData[Code.tex]{rang}\\

\ExecuteMetaData[Code.tex]{ran}

@@

\ExecuteMetaData[Code.tex]{var}\\

\ExecuteMetaData[Code.tex]{sym}

@@

\ExecuteMetaData[Code.tex]{ctx}\\

\ExecuteMetaData[Code.tex]{sctx}\\

\ExecuteMetaData[Code.tex]{ctxdom}\\

\ExecuteMetaData[Code.tex]{ctxidx}\\

\ExecuteMetaData[Code.tex]{elem}

@@

\ExecuteMetaData[Code.tex]{sign}

@@

\ExecuteMetaData[Code.tex]{trees}

@@

\ExecuteMetaData[Code.tex]{H}\\

\ExecuteMetaData[Code.tex]{HHat}\\

\ExecuteMetaData[Code.tex]{V}\\

\ExecuteMetaData[Code.tex]{tensor0}\\

\ExecuteMetaData[Code.tex]{tensor1}\\

\ExecuteMetaData[Code.tex]{extension}
